### 2011-05-04 poster/poster_landscape.tex
Poster: Add logo's and fix rendering bugs

\definecolor{ritorange}{rgb}{0.9529,0.4314,0.1294},
\definecolor{ritbrown}{rgb}{0.9725,0.9686,0.9294},
\definecolor{ritbrownl}{rgb}{0.9765,0.9765,0.9451},
\definecolor{white}{cmyk}{0,0,0,0.0}
\definecolor{black}{cmyk}{0,0,0.0,1.0}

\begin{poster}{
  % Show grid to help with alignment
  grid=no,
  % Column spacing
  colspacing=1em,
  % Color style
  borderColor=black,
  headerColorOne=ritorange,
  headerColorTwo=ritorange,
  headerFontColor=white,
  boxColorOne=ritbrown,
  boxColorTwo=ritbrownl,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=no,
  headerborder=open,
  headerheight=0.08\textheight,
  headershape=roundedright,
  headershade=plain,
  headerfont=\Large\textsf, %Sans Serif
  boxshade=shade-lr,
  background=none,
%  background=shade-tb,
%  background=plain,
  linewidth=1pt
  }
  % Eye Catcher
  {} % No eye catcher for this poster. If an eye catcher is present, the title is centered between eye-catcher and logo.
  % Title
  {\sf %Sans Serif
  %\bf% Serif
  Distrivia: A Distributed Trivia Game}
  % Authors
  {\sf %Sans Serif
  % Serif
  Brian Gianforcaro, Steven Glazer, Samuel Milton\hspace{3em}
  Rochester Institute Of Technology
  }
  % University logo
  {{\begin{minipage}{16em}
    \hfill
    \includegraphics[scale=0.1]{logo}
  \end{minipage}}
  }

@@

\\

@@

%  \headerbox{Funding}{name=funding,column=3,span=1,above=bottom}{

@@

%  This work was supported in part by Microsoft Research through the European PhD Scholarship Programme.
%  }%

@@

% \headerbox{References}{name=references,column=3,above=funding,below=results}{

@@

% }%

>>>>

\definecolor{ritorange}{rgb}{0.9529,0.4314,0.1294}
\definecolor{ritbrown}{rgb}{0.9725,0.9686,0.9294}
\definecolor{ritbrownl}{rgb}{0.9765,0.9765,0.9451}
\definecolor{white}{cmyk}{0,0,0,0.0}
\definecolor{black}{cmyk}{0,0,0.0,1.0}

\begin{poster}{
  % Show grid to help with alignment
  grid=no,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=white,
  bgColorTwo=white,
  borderColor=black,
  headerColorOne=ritorange,
  headerColorTwo=ritorange,
  headerFontColor=white,
  boxColorOne=ritbrown,
  boxColorTwo=ritbrownl,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=no,
  headerborder=open,
  headerheight=0.08\textheight,
  headershape=roundedright,
  headershade=plain,
  headerfont=\Large\textsf, %Sans Serif
  boxshade=shade-lr,
  background=plain,
  linewidth=1pt
  }
  % Eye Catcher
  {} % No eye catcher for this poster. If an eye catcher is present, the title is centered between eye-catcher and logo.
  % Title
  {\sf %Sans Serif
  %\bf% Serif
  Distrivia: A Distributed Trivia Game}
  % Authors
  {\sf %Sans Serif
  % Serif
  \newline
  Brian Gianforcaro, Steven Glazer, Samuel Milton
  - Rochester Institute Of Technology
  }
  % University logo
  {{\begin{minipage}{18em}
    \hfill
    \includegraphics[scale=0.05]{logo}
  \end{minipage}}
  }

@@

@@

  \headerbox{Funding}{name=funding,column=3,span=1,above=bottom}{

@@

  \smaller 
  This work was supported in part by Microsoft Research through the European PhD Scholarship Programme.

@@

 \headerbox{References}{name=references,column=3,above=funding,below=results}{

@@
